\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[margin=0.68in]{geometry}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.32em}

\begin{document}

\begin{center}
    {\Large \textbf{Earnings Surprise, Firm Valuation, and Market Efficiency:}\\[-0.15em]
    \textbf{Evidence from China}}\\[0.2em]
    {\small Team Project Proposal for Corporate Finance (FIN803)}\\[0.1em]
    {\footnotesize Team Members: Yingqi Tan, Zhesheng Xu, Hao Yang}
\end{center}

\small

\noindent\textbf{Project Title.} Earnings Surprise, Firm Valuation, and Market Efficiency: Evidence from China.

\noindent\textbf{Background and Motivation.} Earnings announcements are major information events in capital markets because they update investors' expectations about firms' profitability and value. In this project, \emph{earnings surprise} refers to earnings announcements that exceed prior expectations. A standard implication of an efficient market is that prices should adjust quickly once new information becomes public. However, prior financial research often documents \emph{post-announcement abnormal return} (PAAR), or post-earnings-announcement drift (PEAD), meaning that stocks with positive earnings surprises may continue to earn abnormal returns after the announcement rather than adjusting immediately. This issue is especially relevant in the Chinese stock market, where investor composition, information processing, and market frictions may lead to slower price adjustment.

\noindent\textbf{Research Question.} The central question is whether firms with stronger positive earnings surprises in China experience higher post-announcement abnormal returns. More broadly, we ask whether earnings information is incorporated into stock prices efficiently, or whether delayed adjustment remains economically meaningful after controlling for standard firm characteristics and risk factors.

\noindent\textbf{Relevance to FIN803 Corporate Finance.} This topic is closely aligned with the FIN803 syllabus. First, it relates to \textbf{stock valuation} because earnings news changes expectations about future cash flows and therefore affects intrinsic value. Second, it connects to \textbf{capital markets and the pricing of risk} by distinguishing normal expected return from abnormal return around information events. Third, it uses ideas from \textbf{optimal portfolio theory and CAPM} to benchmark returns and evaluate whether observed post-announcement returns can be explained by systematic risk. Finally, it is relevant to the \textbf{cost of capital} because if market prices do not adjust immediately to earnings information, then measured expected returns and valuation inputs may reflect temporary mispricing as well as risk.

\noindent\textbf{Methodology.} We propose an empirical study using Chinese listed firms and their quarterly or annual earnings announcements. The main explanatory variable will be a measure of earnings surprise, defined as the extent to which reported earnings exceed prior expectations. The main dependent variable will be post-announcement abnormal return over a short window after the earnings release. Abnormal return will be estimated relative to a benchmark such as the market model or CAPM-based expected return. The baseline regression will relate post-announcement abnormal return to earnings surprise, while controlling for firm \(\beta\), firm size, and book-to-market ratio, along with basic time and industry controls where appropriate. A positive and significant coefficient on earnings surprise would indicate that stronger positive surprises are followed by higher abnormal returns. This framework allows us to evaluate whether abnormal returns reflect compensation for risk, as in CAPM and cost of capital, or delayed incorporation of earnings information.

\noindent\textbf{Expected Findings and Contribution.} We expect to find that positive earnings surprises are associated with higher post-announcement abnormal returns, at least over a short horizon, which would be consistent with PEAD, investor underreaction, and delayed price adjustment. Such evidence would suggest that the incorporation of earnings information into stock prices is not fully immediate in the Chinese market. The contribution of the project is to provide a clear Corporate Finance interpretation of this pattern: earnings announcements affect firm valuation, investor reactions may deviate from the fully efficient benchmark, and CAPM-based expected return models can be used to assess whether the observed return continuation reflects risk or delayed information processing. Overall, the project will help evaluate how informative accounting news is for prices and whether market efficiency holds in practice in an important emerging capital market.

\end{document}
