\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{parskip}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=1.5em}
\onehalfspacing

\title{Speaker Script\\Earnings Surprise, Firm Valuation, and Market Efficiency: Evidence from China}
\author{FIN803 Corporate Finance Team}
\date{}

\begin{document}
\maketitle

\section*{Slide 1: Title}
Good afternoon everyone. We are presenting our FIN803 Corporate Finance project on earnings-related information, firm valuation adjustment, and market efficiency in China A-share stocks.

\section*{Slide 2: Motivation}
Our motivation is straightforward: earnings guidance updates expectations of future cash flows, so it should affect valuation. This project is directly aligned with FIN803 topics including stock valuation, capital market pricing of risk, CAPM-based abnormal return measurement, and cost-of-capital intuition.

\section*{Slide 3: Research Question}
Our core question is whether earnings-related guidance events are followed by positive abnormal returns. We emphasize event occurrence effects, and then test whether cross-sectional ranking by our current earnings surprise proxy is stable.

\section*{Slide 4: Firm Valuation and Earnings}
In valuation terms, price reflects discounted expected future cash flows. Earnings disclosures matter because they shift expectations, and market reactions should depend on the gap between realized information and prior expectations.

\section*{Slide 5: Market Efficiency}
Under semi-strong efficiency, public information should be impounded quickly into prices. If we still observe positive post-announcement CAR, that suggests delayed adjustment and potential underreaction.

\section*{Slide 6: Abnormal Returns and CAPM}
We use abnormal return as stock return minus market return. CAPM provides a benchmark intuition for normal required return, and helps us separate event-driven price effects from broad market movement.

\section*{Slide 7: PEAD Intuition}
PEAD means returns continue to drift after earnings news. We test for delayed reaction, but we do not impose a strong monotonic PEAD assumption because our earnings-expectation proxy is imperfect.

\section*{Slide 8: Data Description}
Our sample covers 2020-01-01 to 2026-04-16 in China A-share. The expanded sample includes 800 stocks and 4,980 usable events, with Tushare as the main source and backup/cross-check logic in the pipeline.

\section*{Slide 9: Event Definition}
We use two event types: guidance\_initial and guidance\_upward\_revision. Event timing is the first trading day after announcement, and we avoid duplicate counting within a report-period event timeline.

\section*{Slide 10: Filtering and Tradability}
We apply practical filters: exclude ST stocks, newly listed firms with short trading history, and suspended event-day observations, plus a liquidity filter. These controls reduce noise and make the event sample more tradable.

\section*{Slide 11: Return Measurement}
We compute CAR20 and CAR60 from daily abnormal returns. CAR60 is our main outcome because delayed reaction often appears over a medium post-announcement horizon rather than only immediately.

\section*{Slide 12: Earnings Surprise Proxy}
Our ES measure is guidance midpoint growth minus a consensus-growth proxy. This is not true analyst consensus, so we explicitly treat it as a pragmatic proxy and keep interpretation conservative.

\section*{Slide 13: ES Grouping}
We group events into positive ES, moderate ES (50th--80th percentile within event type), and extreme ES (top 20\%). This allows us to compare economically meaningful categories without overfitting.

\section*{Slide 14: Empirical Strategy}
The design combines event-study averages, group comparisons, and simple regressions. The goal is theory-consistent inference for valuation adjustment, not a trading system.

\section*{Slide 15: Regression Model}
We estimate CAR60 on key signals plus only two basic controls: log size and beta. This keeps the model transparent and aligned with course-level capital market intuition.

\section*{Slide 16: Main Event-Level Results}
At the event level, guidance-related announcements are associated with positive CAR60. In the expanded sample, all-events CAR60 is about 3.02\%, and positive-ES events are about 3.77\%.

\section*{Slide 17: ES Group Comparison}
Moderate ES events have CAR60 around 3.715\%, while extreme ES events are around 5.964\% in this expanded run. The key point is that cross-sectional ranking remains unstable across specifications, so we avoid claiming strict monotonic PEAD.

\section*{Slide 18: Regression Results}
The moderate-ES dummy is positive but statistically insignificant, and the event-type dummy is also insignificant. Although the chart can show a higher raw mean for revision events, the conditional difference is not robust after controls, so we keep a conservative interpretation.

\section*{Slide 19: Corporate Finance Interpretation}
The evidence supports that earnings-related events affect valuation and that market adjustment may be delayed. CAPM controls do not fully explain these short-horizon announcement effects, which is consistent with partial underreaction.

\section*{Slide 20: Limitations and Conclusion}
Our main limitation is measurement of expected earnings without full analyst-consensus coverage. Final takeaway: event-level evidence is more reliable than ES-magnitude ranking, and better expectation measurement is the most important next step.

\end{document}
